\documentclass[letterpaper]{article}

%\usepackage{showframe}
\usepackage[left=0.5cm, right=0.5cm, top=0.5cm, bottom=0.5cm]{geometry}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\usepackage{fancyhdr}
\setlength{\parindent}{0pt}
\usepackage[compact]{titlesec}
\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=blue}
\usepackage{tabu}
\usepackage{mdwlist}
\usepackage[none]{hyphenat}
\usepackage[utf8]{inputenc}

\begin{document}
\begin{center}
{\Huge\textsc{Charlie Li}}

{\small\texttt{\href{mailto:charlie@vishwin.info}{charlie@vishwin.info}~\textbar~\url{https://vishwin.info}~\textbar~\url{https://git.vishwin.info}~\textbar~\url{https://www.linkedin.com/in/vishwin}}}
\rule{\textwidth}{1pt}
\end{center}


\section{Experience}
\begin{tabu}{@{}X[7,l] X[3,r]@{}}
\textbf{Capital One} \textit{Technology Development Intern} & June\textendash August~2015
\end{tabu}
\begin{itemize*}
\item Involved with two Agile teams: a network administration/maintenance team spread across all office locations, and a bank transaction website DevOps team based in Wilmington,~DE
\item Used Flask microframework and D3.js to automatically pull data from the network team's VersionOne kanban board for weekly upper management reports
\item Embedded the above into a new group page for the network team on the company's Jive Software social intranet
\item Corrected some small customer experience issues on the transaction site
\end{itemize*}

\begin{tabu}{@{}X[7,l] X[3,r]@{}}
\textbf{College of IST, Pennsylvania State University} \textit{Learning~Assistant} & August~2014\textendash December~2015
\end{tabu}
\begin{itemize*}
\item Assisted IST~250 twice, once per fall semester. Class focused on fundamental HTML, CSS, JavaScript
\item Assisted IST~256 for Spring~2015, focusing on fundamental CRUD as applicable to the web, mainly PHP and MySQL
\item Both classes primarily online deliverables and assignments, with in-person assistance during scheduled class times and office hours
\item Graded all assignments for all 40\textendash 43~students in IST~250, 27~students in IST~256
\end{itemize*}

\begin{tabu}{@{}X[7,l] X[3,r]@{}}
\textbf{Information Technology Services, Pennsylvania State University} \textit{Lab Consultant} & August~2013\textendash present
\end{tabu}
\begin{itemize*}
\item Assisted users in the campus computer labs with various software and hardware malfunction questions
\item Provided guidance for audio and video editing with iMovie/Final Cut Pro and Garageband
\item Maintained the labs' condition for cleanliness
\item Helped answer other lab consultants' questions when needed
\end{itemize*}


\rule{\textwidth}{0.4pt}
\section{Miscellaneous projects}
\begin{tabu}{@{}X[7,l] X[3,r]@{}}
\textbf{Discovery Space Children's Museum of Central PA} & January\textendash May~2016
\end{tabu}
\begin{itemize*}
\item Coordinated with the Penn State College of Engineering's Engineering Leadership Development Minor programme
\item Repaired their tornado simulation exhibit which suffered from broken fan and faulty wiring
\item Installed a new fan and re-organised wiring setup with a custom printed circuit board, wrote supporting documentation
\end{itemize*}


\rule{\textwidth}{0.4pt}
\section{Hackathon projects}
\begin{itemize*}
\item\textbf{Independence/Jefferson Health Hack~2016}: Intact Birth \textendash~A device to assist hospital staff and patient during the early stages of childbirth to reduce the risk of perineal tearing by massaging. Includes a screen to monitor conditions and regulate massage speed, driven by a Raspberry Pi. Won the Patient Engagement track outright.
\item\textbf{BrickHack~2016}: Brick the HUD \textendash~A heads-up display system for cars. LCD screen on Raspberry Pi beams to a teleprompter glass on windscreen. Designed as a software framework for maximum customisability; uses ncurses as the user interface.
\item\textbf{MHacks~Refactor}: When Craigslist meets MHacks \textendash~An internet-connected hot tub. Hot tub sourced from local Ann Arbor Craigslist, then added Arduino, Intel Edison and Raspberry Pi for acutation and communication respectively. Used two different local area connections for confirmed network separation.
\item\textbf{Fashion/Tech~Hackathon~2016}: SmarterWear \textendash~A pair of women's underwear that includes a smartphone/smartwatch-controlled mild heat pad. Built an Arduino/Tinyduino microcontroller with Bluetooth low energy on the underwear. Won the Most Flashy prize; selected for display in the Kent State University MuseLab.
\item\textbf{DragonHacks~2016}: AmeriToots \textendash~A system that heating oil/gas delivery drivers would use to monitor their customers' usage in order to make prompt replenishments and other emergency repairs as needed. Raspberry Pi as wi-fi access point, Arduino for replaceable tank/monitoring hardware, USB wi-fi dongle in a wok (dish antenna) on the truck.
\item\textbf{HackUMass~2015}: Excitare \textendash~An alarm clock blasting loud music and driving away, prompting the user to actually get out of bed and chase it down to shut it off. Raspberry Pi and speaker on the robotic car kit, Android app to modify Pi's crontab.
\item\textbf{PennApps Spring~2015}: CritSim \textendash~A cycling sensor framework that transmits handlebar force (turn simulation) and wheel spin (instantaneous velocity and distance pedalled) data using a network daemon. Used two Arduinos plus sensors to gather data. Additional inputs, like Sensoria sock, can be added for more data; output can be Oculus/VR and even multiplayer
\end{itemize*}


\rule{\textwidth}{0.4pt}
\section{Education}
\begin{tabu}{@{}X[l] X[r]@{}}
\textbf{Bachelor of Science, Computer Science} (one semester left) \\ The Pennsylvania State University & 2012\textendash attended 2016
\end{tabu}
\end{document}